One more attempt on ArXe

### 2015-07-02 exp_results.tex
correct labels and refs

\section{Experimental Results}
\begin{table}
\caption{
Expansion parameters used for cluster production in this work. Experiments were done with $d = 80~\mu$m (first two sections) and $d = 100~\mu$m (bottom section) conical nozzles of 15$^\circ$ half opening angle. For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given. These values are calculated as in ref.\ \protect\citenum{hagena1981}. Due to the small amount of Xe admixture, we basically have a Xe seeded expansion of Ar gas. We therefore expect actual cluster sizes in-between the two limiting values given. Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model used.
\label{tab:cluster} }

\begin{tabular}{l c c c r r}
%
\toprule
  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
 (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
 (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
 (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
 (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
 (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
  & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 867
1004, 867  & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
868  & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886
886  & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}). It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}. $E_b$ and $w$ are in eV, $A$ is in \%. The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c}
%
\toprule
  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
%
\midrule
% Ar, from Marko
 Ar (1) &  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar (2) &  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 886 & 15.12 & 1.3 & 12.44 & 10.70 & 1.24 & 19\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\section{Experimental Results}

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}). It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}. $E_b$ and $w$ are in eV, $A$ is in \%. The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c}
%
\toprule
  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
%
\midrule
% Ar, from Marko
 Ar (1) &  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar (2) &  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 886 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
\bottomrule
\end{tabular}
\end{table}

### 2015-07-02 experimental.tex

\begin{tabular}{l c c c r r}
%
\toprule
  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
 (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
 (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
 (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
 (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
 (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
  & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 867
1004, 867  & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
868  & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886
886  & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table}
%
%
The apparatus used for the experiments consists of a cooled, supersonic molecular jet apparatus and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation. A detailed description can be found in Ref. \citenum{arion}, and here we focus on those details specific for the current experiment. Commercial Ar and Xe gas was used. Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. Expansion parameters and mean cluster sizes according to an empirical model are given in Tab.\ \ref{tab:cluster}. We note that currently no such empirical model for heterogeneous expansions exists. We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.

The expansion chamber for the supersonic is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. Electrons were detected by a short 'magnetic bottle´ time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} Experiments were carried out at the TGM-4 (last section in Tab.\ \ref{tab:cluster}) and the UE112-PGM-1 (first two sections) beamlines with linearly, horizontally polarized radiation.

>>>>

\begin{tabular}{l c c c r r}
%
\toprule
  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
 (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
 (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
 (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
 (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
 (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
  & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 867
1004, 867  & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
868  & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886
886  & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table}
%
%
The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} A detailed description can be found in Ref. \citenum{arion}, and here we focus on those details specific for the current experiment. Commercial Ar and Xe gas was used. Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. Expansion parameters and mean cluster sizes according to an empirical model are given in Tab.\ \ref{tab:cluster}. We note that currently no such  model for heterogeneous expansions exists. We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.

The expansion chamber for the supersonic is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}). Linearly, horizontally polarized radiation was used.

### 2015-07-02 intro.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%
Electron spectroscopy can make important contributions to the 
research on composition and structure of free nanoparticles.\cite{
jpcc} Besides by photoionization, free electrons emerging from 
nanoparticles can also be produced by the relaxation of 
electronically excited states. One such process, which is of 
particular importance in weakly bonded systems, is the 
Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
cederbaum} In ICD, an electronic excitation decays by energy 
transfer to one of its neighbour atoms or molecules, thus 
releasing a free electron from the latter site. ICD is an 
important relaxation channel e.g. for inner-valence holes in 
elements C-Ne, and also for core levels vacancies e.g. in \ce{H2O}
, where it competes with Auger decay\cite{slavicek}.

@@

Intermolecular Coulombic Decay initially was predicted from 
theoretical considerations of the energy levels in singly vs. 
doubly ionized, and doubly vs. triply ionized, hydrogen bonded 
clusters.\cite{cederbaum} First experimental work some years 
later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
was followed by demonstrations of ICD in a diverse range of other 
systems. Experimental and theoretical progress has been reviewed.
\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
proceeds by an initial ionization producing an ion in an excited 
state, followed by a transfer of energy to a neighbouring site, 
and an electron emission process therefrom. In the final state a 
positive charge remains at the site of ionization, and another 
was created at another atom or molecule. Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
%These were termed `Electron Transfer Mediated Decay' 
% (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
% which the originally excited site is neutralized by the decay, 
% and 'exchange ICD' for charge transfer contributions to the 
% normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization plays a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong (
covalent or metallic) bonding, there is no distinction between 
ICD and Auger decay.\cite{hergenhahn_review}

First experiments on ICD in heterogeneous systems were on Ne-Ar 
clusters.\cite{barthnear} Those were followed by studies of ICD-
like inner-shell decays in aqueous solution.\cite{
aziz,pokapanich,pokapanich2011} Pioneering work also showed the 
potential for studies of the interface between a substrate and an 
adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
clusters was recently presented by some of the authors.\cite{
fasshauer2014} For this system, a detailed analysis of 
photoelectron spectra with respect to structural features of the 
mixed clusters is also available.\cite{lundwall} In Ref. \citenum{
fasshauer2014} it was shown that an analysis of the ICD spectra 
allowed to decide between structural alternatives for which the 
photoelectron data were indiscriminate.

Rare gas clusters are suitable prototype systems for studies of (
e.g.) ICD, as they can easily be produced by supersonic 
expansion. Mixed rare gas clusters easily form by coexpansion of 
the two gases through a cooled nozzle. The size of the clusters 
can be changed by varying the expansion parameters, although for 
heterogeneous clusters some uncertainty remains with respect to 
the cluster size, as empirical scaling laws \cite{hagena1981} 
apply to expansion of pure gases only. Early studies of Ar-Xe 
clusters mostly focussed on the extreme cases of a single Xe atom 
embedded in an Ar cluster (e.g. Ref. \citenum{lengenprl}). 
Different sites of the dopant atom (on top of a surface, 
integrated in an Ar surface, inside the cluster) were 
distinguished by three separate bands in the fluorescence yield 
recorded as a function of excitation wavelength.\cite{lengenprl} 
Increasing the Xe concentration in the expansion lead to changes 
in the fluorescence excitation spectrum that were interpreted as 
formation of \ce{Xe2} and larger Xe complexes inside the clusters.
\cite{lengen} Experiments on Xe-rich mixed clusters were also 
conducted, and concluded that increasing the Xe content in a 
coexpanding ArXe mixture leads to the formation of Xe-core, Ar-
shell systems with a sharp interface between the two species.\cite
{tchaplyguine,hoener} This finding was confirmed by electron 
diffraction experiments.\cite{Danylchenko} Always, the observed 
Xe content in the clusters is above the Xe content in the 
expanding gas mixture, as Xe can be condensed much easier than Ar.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%
Electron spectroscopy can make important contributions to the 
research on composition and structure of free nanoparticles.\cite{
jpcc} Besides photoionization, free electrons emerging from 
nanoparticles can also be produced by the relaxation of 
electronically excited states. One such process, which is of 
particular importance in weakly bonded systems, is the 
Interatomic or Intermolecular Coulombic Decay (ICD).\cite{
cederbaum} In ICD, an electronic excitation decays by energy 
transfer to one of its neighbour atoms or molecules, thus 
releasing a free electron from the latter site. ICD is an 
important relaxation channel e.g. for inner-valence holes in 
elements C-Ne, and also for core levels vacancies e.g. in \ce{H2O}
, where it competes with Auger decay.\cite{slavicek}

@@

Intermolecular Coulombic Decay initially was predicted from 
theoretical considerations of the energy levels in singly vs. 
doubly ionized, and doubly vs. triply ionized, hydrogen bonded 
clusters.\cite{cederbaum} First experimental work some years 
later used Ne clusters,\cite{marburger,jahnkenedimer} but quickly 
was followed by demonstrations of ICD in a diverse range of other 
systems. Experimental and theoretical progress has been reviewed.
\cite{hergenhahn_review, averbukh_review, jahnke_review} ICD 
proceeds by an initial ionization producing an ion in an excited 
state, followed by a transfer of energy to a neighbouring site, 
and an electron emission process therefrom. The final state contains 
two positive charges; one at the original site of ionization, and a second
one at another atom or molecule.

Soon after, related 
autoionization processes were discovered that proceed via a 
charge transfer instead of an energy transfer. 
%These were termed `Electron Transfer Mediated Decay' 
% (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
% which the originally excited site is neutralized by the decay, 
% and 'exchange ICD' for charge transfer contributions to the 
% normal ICD amplitude.\cite{santrarev,jahnkesat}
We find that both energy and charge transfer induced 
autoionization plays a role in Ar-Xe, and will detail the 
relevant processes below. The notion of ICD requires that the 
electronic orbitals of the two sites can be distinguished, which 
typically is the case in weakly bonded systems, held together by 
hydrogen bonds or van-der-Waals bonds. In the case of strong
(covalent or metallic) bonding, it is inpossible to make a
distinction between ICD and Auger decay.\cite{hergenhahn_review}

First experiments on ICD in heterogeneous systems were on Ne-Ar 
clusters.\cite{barthnear} Those were followed by studies of 
ICD-like inner-shell decays in aqueous solution.\cite{aziz,pokapanich,pokapanich2011}
Pioneering work also showed the 
potential for studies of the interface between a substrate and an 
adsorbate by ICD.\cite{grieves} More detailed work on Ne-Ar 
clusters was recently presented by some of the authors.\cite{
fasshauer2014} For that system, a detailed analysis of 
photoelectron spectra with respect to structural features of the 
mixed clusters is also available.\cite{lundwall} In Ref. \citenum{
fasshauer2014} it was shown that an analysis of the ICD spectra 
allowed to decide between structural alternatives for which the 
photoelectron data were indiscriminate.

Rare gas clusters are suitable prototype systems for studies of
(e.g.) ICD, as they can readily be produced by supersonic 
expansion. Mixed rare gas clusters easily form by coexpansion of 
the two gases through a cooled nozzle. The size of the clusters 
can be changed by varying the expansion parameters, although for 
heterogeneous clusters some uncertainty remains with respect to 
the cluster size, as empirical scaling laws \cite{hagena1981} 
apply to expansion of pure gases only. Early studies of Ar-Xe 
clusters mostly focussed on the extreme cases of a single Xe atom 
embedded in an Ar cluster (e.g. Ref. \citenum{lengenprl}). 
Different sites of the dopant atom (on top of a surface, 
integrated in an Ar surface, inside the cluster) were 
distinguished by three separate bands in the fluorescence yield 
recorded as a function of excitation wavelength.\cite{lengenprl} 
Increasing the Xe concentration in the expansion lead to changes 
in the fluorescence excitation spectrum that were interpreted as 
formation of \ce{Xe2} and larger Xe complexes inside the clusters.
\cite{lengen} Experiments on Xe-rich mixed clusters were also 
conducted, and concluded that increasing the Xe content in a 
coexpanding ArXe mixture leads to the formation of Xe-core, 
Ar-shell systems with a sharp interface between the two species.\cite
{tchaplyguine,hoener} This finding was confirmed by electron 
diffraction experiments.\cite{Danylchenko} Always, the observed 
Xe content in the clusters is above the Xe content in the 
expanding gas mixture, as Xe can be condensed much easier than Ar.
A complementary study used photoelectron-photoion coincidence of
large Ar-Xe clusters, and found that after inner shell (Xe 4d, Ar 2p)
photoionization significant charge transfer between both species
occurs before the mass spectroscopic final state is reached.\cite{berrah}

### 2015-07-02 theory.tex
correct refs

\section{Theoretical Approach}
Experimental coincidence spectra are given by the kinetic energies $E_{sec}$
of the secondary electron
and the intensities of the peaks. The latter is proportional to the
probability of the decay as well as the theoretically determinable
decay width $\Gamma=\frac{\hbar}{\tau}$,
which is inverse proportional to the lifetime $\tau$. The manifold of the
secondary energies and decay widths will therefore compose the electron-electron
coincidence spectrum.
In case of noble gas clusters
with given structures three aspects have to be taken into account:
different decay mechanisms, the possibility to decay with multiple
interaction partners and different decay channels within each decay mechanism.
At the current stage of development we need to neglect the nuclear dynamics which
additionally might play an important role.

@@

\begin{equation}
 \Gamma_{ICD,i,\beta} = 2\pi
                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}}
\end{equation}

>>>>

\section{Theoretical Approach}
%
Experimental coincidence spectra are given by the kinetic energies $E_{sec}$
of the secondary electron
and the intensities of the peaks. The latter is proportional to the
probability of the decay as well as the theoretically determinable
decay width $\Gamma=\frac{\hbar}{\tau}$,
which is inverse proportional to the lifetime $\tau$. The manifold of the
secondary energies and decay widths will therefore compose the electron-electron
coincidence spectrum.
In case of noble gas clusters
with given structures three aspects have to be taken into account:
different decay mechanisms, the possibility to decay with multiple
interaction partners and different decay channels within each decay mechanism.
At the current stage of development we need to neglect the nuclear dynamics which
additionally might play an important role.

@@

\begin{equation}
 \Gamma_{ICD,i,\beta} = (2J_{in}+1) \frac{3c^4}{8\pi}
                        \sum\limits_{M_{in}'}
                        \left| \left(
                        \begin{array}{ccc}
                        J_A'  & 1        & J_A\\
                        -M_A' & M_A'-M_A & M_A
                        \end{array}\right) \right|^2
                        \frac{\sigma^{(X_E)}(\omega_{vp,\beta})}
                        {R_i^6 \, \omega_{vp,\beta}^4 \tau_{in,\beta}}
\end{equation}
